Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-06-28 main.tex
Add example with concrete numbers

>>>>

To illustrate the effect of the balance-assist system on fall probability, we will
give an example of how the data collected during the experiments is used to predict
fall probability. We use \ref{eq:log-regress} and the coefficients in 
\ref{tab:freq-coefs-6}. For simplicities sake, the interaction effects are not included.
Let's assume that the mean angular impulse $\bar{L}$ of all the perturbations applied to 
a participant is 100~\si{\newton}, and the standard deviation $\sigma^{L}=15$. The centred
and scaled angular impulse can be calculated by substracting $\bar{L}$ from the applied
angular impulse $L$, and dividing this by $\sigma^{L}$. The same applies for the 
perturbation order $c$, initial roll angle $\phi_0$ and initial steer angle $\delta_0$.
If we take the coefficients estimated for cycling at 6~\si{\kilo\meter\per\hour}, the
log-odds of falling can be calculated as follows.

\begin{align}
	\log \left( \frac{p_{ij}}{1-p_{ij}} \right) & = \beta + \sum_{k}^{k=0}\alpha_k 
	\frac{x_{ij}^{k}-\bar{x_{ij}^{k}}} {\sigma^{x^{k}}} 
	& = -0.29 + 1.69\cdot\frac{110~\si{\newton} - 115\si{\newton}}{15\si{\newton}} 
	-0.77\cdot\frac{10-20}{11.54} 
	-0.25\cdot\frac{-6\si{\degree}-2\si{\degree}}{10\si{\degree}} 
	-0.14\cdot\frac{1\si{\degree}+3\si{\degree}}{5\si{\degree}}
	-0.64\cdot s
	& = 1.42 -0.64 \cdot s
\end{align}

The state of the balance-assist $s$ is a binary variable. If the balance-assist is turned on, 
the log-odds that a fall occurs are decreased by 0.64. The odds and probability can be calculated:

\begin{align}
	\frac{p_{ij}}{1-p_{ij}} = e^{1.42-0.64s} = e^{1.42}\cdot e^{-0.64s} = 4.14 \cdot 0.53s
\end{align}

\begin{align}
	p_{ij}^{s=0} = \frac{4.14}{1 + 4.14} = 0.81
\end{align}

\begin{align}
	p_{ij}^{s=1} = \frac{4.14\cdot0.53}{1 + 4.14\cdot{0.53}]} = 0.69
\end{align}

Turning on the balance-assist system reduces the probability that the perturbation results in a 
fall from 0.81 to 0.69.
